Asimilación de distintas observaciones

### 2020-12-17 analysis/chapters/experimento_20181122.Rmd
Figura reflectividad

ppacum_1h %>% 
.[, .(prop = mean(prop)), by = .(exp, date, y, umbral)] %>% 
  .[umbral %in% c(1, 5)] %>% 
ggplot(aes(date, y)) +
  geom_contour_fill(aes(z = prop*100, fill = stat(level)),
                    breaks = seq(0, 100, 10)) +
  scale_color_gradientn(colours = rev(Redmonder::redmonder.pal(10, name = "qMSOStd")), 
                       limits = c(10, 100),
                       na.value = "white",
                       super = ScaleDiscretised,
                       breaks = seq(0, 100, 10),
                       guide = guide_colorstrip(barwidth = 15,
                                                barheight = 1)) +
  # scale_date() +
  labs(fill = "", x = "", y = "") +
  facet_grid(umbral~exp) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

>>>>

ppacum_1h %>% 
  .[, .(prop = mean(prop)), by = .(exp, date, y, umbral)] %>% 
  .[umbral %in% c(1, 5)] %>% 
  ggplot(aes(date, y)) +
  geom_contour_fill(aes(z = prop*100, fill = stat(level_d)),
                    breaks = seq(0, 100, 10)) +
  scale_fill_gradientn(colours = rev(Redmonder::redmonder.pal(10, name = "qMSOStd")),
                       limits = c(10, 100),
                       na.value = "white",
                       super = ScaleDiscretised,
                       # breaks = seq(0, 100, 10),
                       guide = guide_colorsteps(barwidth = 15,
                                                barheight = 1)) +
  # scale_color_viridis_c() +
  scale_date(ini = 20181121000000, break_bin = "12 hours") +
  facet_grid(umbral ~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                       E6 = "SATWND", E7 = "RAD"),
                                               umbral = c("1" = "1 mm/h",
                                                          "5" = "5 mm/h"))) +
  labs(fill = "", x = "", y = "") +
  theme_minimal() +
  theme(legend.position = "bottom")
```

#### Reflectivity

```{r}

dates <- rep(c("20181122100000", "20181122220000"), 1, each = 4)
files <- paste0(derived_data, "dbz/maxdbz_ana_", experiments, "_", dates, ".nc")

dbz <- purrr::map(files, function(f){

  meta <- unglue(basename(f), "maxdbz_ana_{exp}_{date}.nc")
  ReadNetCDF(f, vars = c(lon = "XLONG", lat = "XLAT", "max_dbz")) %>% 
    .[, ":="(exp = meta[[1]][["exp"]],
             date = ymd_hms(meta[[1]][["date"]]))] %>% 
    .[, c("x", "y") := wrf_project(lon, lat)] 
}) %>% 
  rbindlist()

dbz %>% 
  .[, date := factor(date)] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = max_dbz, fill = stat(level_d)), 
                    proj = norargentina_lambert,
                    breaks = seq(0, 60, 5),) +
  scale_color_dbz(aesthetics = "fill", super = ScaleDiscretised, 
                  guide = guide_colorsteps(barheight = 18)) +
  geom_mapa() +
  facet_grid(date~exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                   E6 = "SATWND", E7 = "RAD"))) +
  labs(x = NULL, y = NULL, fill = NULL) +
  theme_minimal()
```
